{ \fontfamily{ptm}\selectfont Error Bound Can Give Near Optimal Convergence Rate for Inexact Accelerated Proximal Gradient Method }

### 2025-10-28 Notebook LaTEX/Inexact AGP made simple for applications/main.tex
>w<, changes

    \subsection{Epsilon subgradient and inexact proximal point}

@@

@@

        This problem admits dual objective in $\RR^m$: 

@@

            \Psi_\lambda(v) &:=
            \frac{1}{2\lambda}\Vert \lambda A^\top v - y\Vert^2

@@

        If strong duality holds, it exists $(\hat u, \hat v)$ such that we have the following: 

@@

        \todoinline{Cette propositions ira démontrer que le séquence de ``Inexact Gradient Mapping" converge. }

@@

            Assume inductively that $\alpha_k \in (0, 1]$. 
            We can solve for $\alpha_k$ using the recursive equality from Assumption \ref{ass:opt-mmntm-seq} which always has one of the strictly positive root given by: 
                &= \frac{\alpha_{k - 1}^2L_{k - 1}}{2L_k}\left(
                    - 1 + \left(
                        1 + \frac{4 L_k}{L_{k - 1}\alpha_{k-1}^2}
                &\underset{(1)}{<} \frac{\alpha_{k - 1}^2L_{k - 1}}{2L_k}\left(
                    - 1 + 1 + 2 \alpha_{k - 1}^{-2}\frac{L_k}{L_{k - 1}}

@@

            At (1) we completed a square inside the radical, and use the assumption that $\alpha_k > 0$ and, $L_k > 0, L_{k - 1} > 0$ because we had $B_k > 0$: 
                1 + 4 L_{k}L_{k - 1}^{-1}\alpha_{k - 1}^{-2}
                1 + 4 L_{k}L_{k - 1}^{-1}\alpha_{k - 1}^{-2}
                + 2L_k^2L_{k - 1}^{-2}\alpha_{k - 1}^{-4}
                - 2L_k^2L_{k - 1}^{-2}\alpha_{k - 1}^{-4}
                &= (1 + 2L_kL_{k - 1}^{-1}\alpha_{k - 1}^{-2})^2
                - 2\alpha_{k - 1}^{-4}L_k^2L_{k - 1}^{-2}
                &< \left(1 + 2L_kL_{k - 1}^{-1}\alpha_{k - 1}^{-2}\right)^2. 
            To see that $\alpha_k > 0$, recall the same fact that $L_k > 0$, and use the inductive hypothesis that $\alpha_{k - 1} \in (0, 1]$ then $\alpha_k > 0$ because: 
                &\ge \frac{L_{k - 1}}{2L_k}\left(
                        \alpha_{k - 1}^4
                &> 0. 

@@

                \frac{L_{k - 1}\alpha_0^2L_0}{L_k}

@@

                (\beta_k\beta_{k - 1}^{-1})\beta_{k - 1}L_0\alpha_0^2L_k^{-1}

@@

            Since $\beta_i$ is monotone decreasing, it has $0 < \beta_i^{-1/2}\beta_{i - 1}^{-1/2} \le 1$, this gives: 

@@

            Performing a telescoping sum, use the fact that $\beta_0 = 1$ will yield the desired results after some algebraic manipulations. 

@@

                \right)^{-2} \ge \mathcal O(k^{-2-p}). 

@@

                &\ge \mathcal O(k^{-2-p}). 

@@

    The inner loop of the algorithm is another algorithm that evaluates $x_k \approx_\epsilon T_{(B_k + \rho_k)}(y_k)$ for a given value of $\epsilon, B + \rho$ and at the point $y_k$. 
    To accomplish, let $\lambda = (B_k + \rho_k)^{-1}$, the algorithm needs to resolve the following equivalent inexact proximal point problem: 

@@

@@

    \begin{definition}[proximal gradient method]\label{def:ista}

@@

            The algorithm that solves the proximal problem generates the primal dual sequences $(z_n, v_n)$ such that for all $n = 0, 1, 2, \cdots$, by the rules: 
                v_{n + 1} &= \hprox_{\tau^{-1} \omega^\star}\left(
                    v_{n} - \tau^{-1}\nabla h(v_n)

@@

                z_{n + 1} &= y - \lambda A^\top v_{n + 1}. 
            Terminates if $\mathbf G_\lambda(z_n, v_n) \le \epsilon$ where $\mathbf G_\lambda$ is given by \eqref{eqn:duality-gap-pp}. 

@@

            The value of $\mathbf G_\lambda(z_n, v_n)$ is easy to compute, it only requires access to matrix $A, A^\top$, and the function $\omega$. 

@@

            The gradient $\nabla f(v)$ is easy to compute, and it is: $AA^T v - Ay$.

@@

            Let $\tau$, $v_0, \epsilon$ be given by an algorithm that satisfies Definition \ref{def:ista-inner-lp} and, it generates iterates $(z_n, v_n)_{n \ge 0}$. 

@@

                \item The sequence $\Psi_\lambda(v_n) - \Psi_\lambda(\bar v)$ converges linearly to zero. \label{prop:inn-looplin-cnvg-item1}
                \item If we let $\bar z := y - \lambda A^\top \bar v$, then $\Phi_\lambda(z_n) - \Phi_\lambda(\bar z)$ converges linearly to zero. \label{prop:inn-looplin-cnvg-item2}
                \item The duality gap has convergence $\mathbf G_\lambda(z_n, v_n) \le \mathcal O\left(\left(1 - \frac{\gamma_\lambda}{2\tau}\right)^{n/2}\right)$. \label{prop:inn-looplin-cnvg-item3}
                \item If $\mathbf G_\lambda(z_n, v_n) \le \epsilon$, then $z_n \approx_\epsilon \hprox_{\lambda g}(y)$. \label{prop:inn-looplin-cnvg-item4}

@@

            Note that $\Psi_\lambda$ satisfies error bound condition in Assumption \ref{ass:lin-cnvg-for-pp}, and Definition \ref{def:ista-inner-lp} has $\tau \ge \lambda\Vert A^TA\Vert$ which satisfies Definition \ref{def:ista} therefore the linear convergence results of Theorem \ref{thm:lin-cnvg-ista-eb} applies to $\Psi_\lambda(v_n) - \Psi_\lambda(\bar v)$. 

@@

                \Psi_\lambda(v_n) - \Psi_\lambda(\bar v) &\le 

@@

                \right)^n

@@

            Recall that the iterates $z_n = y - \lambda A^\top v_n$, and $\bar z = y - \lambda A^\top \bar v$, and we have Lipschitz continuity of $\Phi_\lambda$, hence Theorem \ref{fact:minimizing-dual-pp} applies, in addition since $\Phi_\lambda$ were assumed to be globally Lipschitz on $\dom \Phi_\lambda$ in Assumption \ref{ass:lin-cnvg-for-pp}, this means that we can replace $K$ regardless of $\bar v$, and convergent primal sequence $z_n \rightarrow \bar z$ with $L_\Phi^\lambda$ which gives: 

@@

                    \Phi_\lambda(z_n) - \Phi_\lambda(\bar z) &\le L_\Phi^\lambda \sqrt{2\lambda}\left(
                    \Psi_\lambda(v_n) - \Psi_\lambda (\bar v)

@@

                    \right)^{n/2}\left(

@@

                & \mathbf G_\lambda(z_n, v_n) 
                &\underset{(1)}{=} \Phi_\lambda(z_n) + \Psi_\lambda(v_n) + 0
                &= \Phi_\lambda(z_n) + \Psi_\lambda(v_n) - \Phi_\lambda(\bar z) - \Psi_\lambda(\bar v)
                &= \Phi_\lambda(z_n)- \Phi_\lambda(\bar z) + \Psi_\lambda(v_n) - \Psi_\lambda(\bar v)

@@

                \right)^{n}\left(

@@

                    \right)^{n/2} (\Psi_\lambda(v_0) - \Psi_\lambda(\bar v))

@@

        The next proposition will characterize a precise case where Assumption \ref{ass:lin-cnvg-for-pp} is true, and it's a case widely available in applications. 
        \begin{proposition}[1-norm problem]\label{prop:1nrm-prox-problem}
            In addition, if $g := \Vert \cdot\Vert_1$, then the function $\Psi_\lambda, \Phi_\lambda$ satisfies Assumption \ref{ass:lin-cnvg-for-pp}. 
            To verify, it requires that
                \item The function $\Psi_\lambda$ satisfies the error bound condition as specified in Assumption \ref{ass:pg-eb}; 
                \item $\Psi_\lambda$ is also a Lipschitz continuous function. 
            Take note that the dual has closed form $g^\star(z) =\delta(z | \{x : \Vert x\Vert_1 \le 1\})$. 
            The $g^\star$ is an indicator of a polytope constraint. 
            The objective function $\Psi_\lambda(v) = \frac{1}{2\lambda}\Vert \lambda A^\top v - y\Vert^2 + \omega^\star(v) - \frac{1}{2\lambda}\Vert y\Vert^2$ so it's Lipschitz continuous on its domain, and it must have a set of minimizers $S$ because its domain is compact. 
            In addition, $\Psi_\lambda$ fits the assumption of Necoara et al. \cite[Theorem 8]{necoara_linear_2019}. 
            Therefore, $\Psi_\lambda$ is quasi-strongly convex then by \cite[Theorem 4]{necoara_linear_2019}, and \cite[Theorem 7]{necoara_linear_2019}, it satisfies error bound condition as given in Assumption \ref{ass:pg-eb}, hence Assumption \ref{ass:lin-cnvg-for-pp} also. 
            Let $\mu_f = \Vert A\Vert^2/\kappa_f$, let $\kappa_f = \theta^{-2}(A, C)$ be the Hoffman Constant as presented by Necoara et al. in \cite[Section 4]{necoara_linear_2019} where $C$ is the constraint matrix of the inequality set $\delta(z | \{x : \Vert x\Vert_1 \le 1\})$, then the error bound constant can be satisfied with
                \gamma_\lambda = \frac{\kappa_f}{1 + \lambda\mu_f + \sqrt{1 + \lambda\mu_f}}. 
            It is very difficult to obtain a lower estimate for $\gamma$ in practice. 
        \begin{definition}[piecewise linear-quadratic function {\cite[Definition 10.20]{rockafellar_variational_1998}}]
            A function $f: \RR^n \rightarrow \overline \RR$ is piecewise linear-quadratic when $\dom f$ is the union of finitely many piecewise polyhedral set, such that on each polyhedral partition of $f$ there exists $\alpha \in \RR, a \in \RR^n$, $C\in \RR^{n \times n}$ as a symmetric matrix is where $f$ has the representation $x \rightarrow \langle x, Cx\rangle + \langle a, x\rangle + c$. 
        The following proposition characterizes another case where error bound conditions of problem holds. 
        \begin{proposition}[convex PLQ proximal problem]\label{prop:plq-pp}

@@

            For any integer $k \ge 0$, this assumption is about parameters of the proximal problem $\left(g, \omega, A, \tilde y_k, \Phi_\lambda^{(k)}, \Psi_\lambda^{(k)}, L^{\lambda, (k)}_{\Phi} ,\gamma_\lambda^{(k)}\right)$ introduced at the beginning of this section, iterates $\left(z_n^{(k)}, v_n^{(k)}\right)_{n\ge0}$, the primal dual solutions $\left(\bar z^{(k)}, \bar v^{(k)}\right)$ and additional parameters $\lambda^{\min}, \lambda^{\max}, \gamma^{\min}, C_0$. 

@@

                \item The iterates of the inner loop $(z_n^{(k)}, v_n^{(k)})_{k \ge 0}$ are produced by an algorithm that satisfies Definition \ref{def:ista-inner-lp}. 

@@

            Let $\left(g, \omega, A, \tilde y_k, \Phi_\lambda^{(k)}, \Psi_\lambda^{(k)}, L^{\lambda, (k)}_{\Phi} ,\gamma_\lambda^{(k)}\right)$, $\left(z_n^{(k)}, v_{n}^{(k)}\right)_{n \ge 0}$, $\left(\bar z^{(k)}, \bar v^{(k)}\right)$ and additional parameters $\lambda^{\min}, \lambda^{\max}, \gamma^{\min}, C_0$ such that they satisfy Assumption \ref{ass:bounded-inn-cmplx}. 

@@

                Denote $N_\epsilon$ to be the total number of iteration of inner loop needed to achieve $\mathbf G_\lambda^{(k)}(z_n, v_n) \le \epsilon$, then it's sufficient to have 

@@

                & \mathbf G_\lambda^{(k)}(z_n^{(k)}, v_n^{(k)}) 

@@

                \right)^{n/2}

@@

                \right)^{n/2} C_2

@@

                \right)^{n/2} C_2. 

@@

            Now, substitute $n = N_\epsilon$ then it's prominent that $\mathbf G_\lambda^{(k)}\left(z_n^{(k)}, v_n^{(k)}\right) \le \epsilon$ by using the log of base formula. 

@@

>>>>

    \subsection{Preliminaries}

@@

        \begin{fact}[Fenchel Rockafellar duality]

@@

        Observe that $\rng A \cap \reli\dom g \neq\emptyset$ in Assumption \ref{ass:for-inxt-prox} shows $g$ is also closed convex and proper. 
        The function $\Phi_\lambda$ is coersive due to its quadratic term and hence it must admit a minimizer \cite[Theorem 1.9]{rockafellar_variational_1998}. 
        Recall the following famous theoretical result in the convex programming literature that we had adapted into our context. 
        \begin{fact}[French Rockafellar Duality {\cite[Proposition 15.22]{bauschke_convex_2017}}]\;\label{fact:fn-rck-duality}\\
            Let $f:\RR^n \rightarrow \overline \RR$ be closed convex and proper, $g: \RR^m \rightarrow \overline \RR$, $A \in \RR^{m \times n}$. 
            If ${\mathbf 0 \in \inte(\dom g - A \dom f)}$, then 
                \inf_{u\in \RR^n}\left\lbrace
                    f(u) + g(Au)
                \right\rbrace 
                + \min_{v \in \RR^m}\left\lbrace
                    f^\star\circ(-A^\top) + g^\star(v)
                \right\rbrace = 0. 
            The theorem is not exactly the same as what is claimed in the original text, since we are in a finite dimensional setting.
            To see the original theorem cited in the finite dimension, we need the space $\mathcal H = \RR^n$ and then use \cite[Proposition 6.12]{bauschke_convex_2017}. 
        In our context, we are interested in the dual of the proximal problem $\Phi_\lambda$ which makes $f = u \mapsto \frac{1}{2\lambda}\Vert u - y\Vert^2$, and $g = \omega$, and it has $f^\star(v) = \frac{1}{2\lambda}\Vert \lambda v + y\Vert^2 - \frac{1}{2\lambda}\Vert y\Vert^2$ (see Apendix \ref{lemma:chore1}). 
        Consequently, $[f^\star \circ (- A^\top)](v) = \frac{1}{2\lambda}\Vert -\lambda A^\top v  + y\Vert^2 - \frac{1}{2\lambda}\Vert y\Vert^2$. 
        And therefore, $\Phi_\lambda$ admits Fenchel Rockafellar dual (or simply the dual) objective in $\RR^m$: 

@@

            \Psi_\lambda(v) &:= f^\star\circ(-A^\top) + g^\star(v) 
            = \frac{1}{2\lambda}\Vert \lambda A^\top v - y\Vert^2

@@

        Note that in this case the smooth part is quadratic and, $\dom f = \RR^n$, hence it translates to ${\mathbf 0 \in \inte(\dom g - A \dom f) = \inte(\dom g - \rng A)}$. 
        This will hold because of $\rng A \cap \reli\dom g \neq\emptyset$ in Assumption \ref{ass:for-inxt-prox}.
        Therefore strong duality holds and it exists $(\hat u, \hat v)$ such that we have the following: 

@@

        \todoinline{Cette proposition ira démontrer que le séquence de ``Inexact Gradient Mapping" converge. }

@@

            Fix any $k \ge 1$. 
            Assume inductively that $\alpha_{k - 1} \in (0, 1]$. 
            We can solve for $\alpha_k$ using the recursive equality $(1 - \alpha_k) = \alpha_{k}^2L_k\alpha_{k - 1}^{-2}L_{k - 1}^{-1}$ from Assumption \ref{ass:opt-mmntm-seq}.
            Writing $\alpha_{k - 1}$ as $\alpha$, and $L_k/L_{k - 1}$ as $q$.
            We then solve for $\alpha_{k}$, the quadratic equation always admits one root that is strictly positive which is given as: 
                \alpha_k &= \frac{1}{2}\left(
                    - \frac{\alpha^2}{q} + \sqrt{
                        \frac{\alpha^4}{q^2} + \frac{4\alpha^2}{q}
                &= \frac{\alpha^2}{2q}\left(
                    - 1 + \sqrt{1 + \frac{4q}{\alpha^2}}
                &\underset{(1)}{<}
                \frac{\alpha^2}{2q}\left(
                    -1 + 1 + \frac{2q}{\alpha^2}

@@

            At (1) we completed a square in the radical, and we used the assumption $\alpha_k > 0$ and, $L_k > 0, L_{k - 1} > 0$ because we had $B_k > 0$, therefore the following chain of inequality holds: 
                1 + \frac{4q}{\alpha^2} &= 
                1 + \frac{4q}{\alpha^2} + \frac{4q^2}{\alpha^4} - \frac{4\alpha^2}{\alpha^2}
                    1 + \frac{2q}{\alpha^2}
                \right)^2 - \frac{4q^2}{\alpha^4} 
                &< \left(
                    1 + \frac{2q}{\alpha^2}  
            To see that $\alpha_k > 0$, recall the same fact that $L_k > 0$, and the inductive hypothesis $\alpha_{k - 1} \in (0, 1]$ then $4q/\alpha^2 > 0$ so obviously $\alpha_k = \frac{\alpha^2}{2q}\left(-1 + \sqrt{1 + 4q/\alpha^2}\right) > 0$ because the quantity inside the radical is strictly larger than $1$. 

@@

                \frac{\alpha_0^2L_0}{L_k}

@@

                (\beta_k\beta_{k - 1}^{-1})\left(
                    \beta_{k - 1}
                \right)L_0\alpha_0^2L_k^{-1}

@@

            Since $\beta_i$ is monotone decreasing, it has $0 < \beta_i^{1/2}\beta_{i - 1}^{-1/2} \le 1$, this gives: 

@@

            Performing a telescoping sum for $i = 1, 2, \ldots, k$, use the fact that $\beta_0 = 1$ will yield the desired results after some algebraic manipulations. 

@@

                \right)^{-2} = \mathcal O(k^{-2-p}). 

@@

                &= \mathcal O(k^{-2-p}). 

@@

    The inner loop is another algorithm that evaluates $x_k \approx_\epsilon T_{(B_k + \rho_k)}(y_k)$ for a given value of $\epsilon, B + \rho$ and at the point $y_k$. 
    To accomplish let's assume that the outer loop iteration $k$ is fixed throughout this entire section.
    Now let $\lambda = (B_k + \rho_k)^{-1}$, the algorithm needs to resolve the following equivalent inexact proximal point problem: 

@@

        \begin{align}\label{ineq:pg-eb}

@@

    \begin{definition}[proximal gradient method]\;\label{def:ista}\\

@@

            The algorithm that solves the proximal problem generates the primal dual sequences $(z_j, v_j)$ such that for all $j = 0, 1, 2, \cdots$, they satisfy: 
                v_{j + 1} &= \hprox_{\tau^{-1} \omega^\star}\left(
                    v_{j} - \tau^{-1}\nabla h(v_j)

@@

                z_{j + 1} &= y - \lambda A^\top v_{j + 1}. 
            Terminates if $\mathbf G_\lambda(z_j, v_j) \le \epsilon$ where $\mathbf G_\lambda$ is given by \eqref{eqn:duality-gap-pp}. 

@@

            The value of $\mathbf G_\lambda(z_j, v_j)$ is easy to compute, it only requires access to matrix $A, A^\top$, and the function $\omega$. 

@@

            The gradient $\nabla f(v)$ is easy to compute, and it is: $AA^\top v - Ay$.

@@

            Let $\tau$, $v_0, \epsilon$ be given by an algorithm that satisfies Definition \ref{def:ista-inner-lp} and, it generates iterates $(z_j, v_j)_{j \ge 0}$. 

@@

                \item The sequence $\Psi_\lambda(v_j) - \Psi_\lambda(\bar v)$ converges linearly to zero. \label{prop:inn-looplin-cnvg-item1}
                \item If we let $\bar z := y - \lambda A^\top \bar v$, then $\Phi_\lambda(z_j) - \Phi_\lambda(\bar z)$ converges linearly to zero. \label{prop:inn-looplin-cnvg-item2}
                \item The duality gap has convergence $\mathbf G_\lambda(z_j, v_j) \le \mathcal O\left(\left(1 - \frac{\gamma_\lambda}{2\tau}\right)^{j/2}\right)$. \label{prop:inn-looplin-cnvg-item3}
                \item If $\mathbf G_\lambda(z_j, v_j) \le \epsilon$, then $z_j \approx_\epsilon \hprox_{\lambda g}(y)$. \label{prop:inn-looplin-cnvg-item4}

@@

            Note that $\Psi_\lambda$ satisfies error bound condition in Assumption \ref{ass:lin-cnvg-for-pp}, and Definition \ref{def:ista-inner-lp} has $\tau \ge \lambda\Vert A^TA\Vert$ which satisfies Definition \ref{def:ista} therefore the linear convergence results of Theorem \ref{thm:lin-cnvg-ista-eb} applies to $\Psi_\lambda(v_j) - \Psi_\lambda(\bar v)$. 

@@

                \Psi_\lambda(v_j) - \Psi_\lambda(\bar v) &\le 

@@

                \right)^j

@@

            Recall that the iterates $z_j = y - \lambda A^\top v_j$, and $\bar z = y - \lambda A^\top \bar v$, and we have Lipschitz continuity of $\Phi_\lambda$, hence Theorem \ref{fact:minimizing-dual-pp} applies, in addition since $\Phi_\lambda$ were assumed to be globally Lipschitz on $\dom \Phi_\lambda$ in Assumption \ref{ass:lin-cnvg-for-pp}, this means that we can replace $K$ regardless of $\bar v$, and convergent primal sequence $z_j \rightarrow \bar z$ with $L_\Phi^\lambda$ which gives: 

@@

                    \Phi_\lambda(z_j) - \Phi_\lambda(\bar z) &\le L_\Phi^\lambda \sqrt{2\lambda}\left(
                    \Psi_\lambda(v_j) - \Psi_\lambda (\bar v)

@@

                    \right)^{j/2}\left(

@@

                & \mathbf G_\lambda(z_j, v_j) 
                &\underset{(1)}{=} \Phi_\lambda(z_j) + \Psi_\lambda(v_n) + 0
                &= \Phi_\lambda(z_j) + \Psi_\lambda(v_j) - \Phi_\lambda(\bar z) - \Psi_\lambda(\bar v)
                &= \Phi_\lambda(z_j)- \Phi_\lambda(\bar z) + \Psi_\lambda(v_n) - \Psi_\lambda(\bar v)

@@

                \right)^{j}\left(

@@

                    \right)^{j/2} (\Psi_\lambda(v_0) - \Psi_\lambda(\bar v))

@@

    \subsection{Concrete examples where we can have linear convergence}
        Some results in the literature ensuite.  
        \begin{definition}[quasi-strongly convex function]

        \end{definition}
        \begin{definition}[quadratic growth]

        \end{definition}
        \begin{fact}[error bound quadratic growth equivalence]

        \end{fact}
        \begin{fact}[Hoffman error bound]

        \end{fact}
        The next proposition will characterize a precise case where Assumption \ref{ass:lin-cnvg-for-pp} is true, and it's a case widely available in applications. 
        \begin{proposition}[1-norm problem]\label{prop:1nrm-prox-problem}
            Let $(g, \omega, A)$ satisfies Assumption \ref{ass:for-inxt-prox}. 
            In addition, if $g := \Vert \cdot\Vert_1$, then the function $\Psi_\lambda, \Phi_\lambda$ satisfies Assumption \ref{ass:lin-cnvg-for-pp}. 
        \end{proposition}
        \begin{proof}
            To verify, it requires that
            \begin{enumerate}[nosep]
                \item The function $\Psi_\lambda$ satisfies the error bound condition as specified in Assumption \ref{ass:pg-eb}; 
                \item $\Psi_\lambda$ is also a Lipschitz continuous function. 
            \end{enumerate}
            Take note that the dual has closed form $g^\star(z) =\delta(z | \{x : \Vert x\Vert_1 \le 1\})$. 
            The $g^\star$ is an indicator of a polytope constraint. 
            The objective function $\Psi_\lambda(v) = \frac{1}{2\lambda}\Vert \lambda A^\top v - y\Vert^2 + \omega^\star(v) - \frac{1}{2\lambda}\Vert y\Vert^2$ so it's Lipschitz continuous on its domain, and it must have a set of minimizers $S$ because its domain is compact. 
            In addition, $\Psi_\lambda$ fits the assumption of Necoara et al. \cite[Theorem 8]{necoara_linear_2019}. 
            Therefore, $\Psi_\lambda$ is quasi-strongly convex then by \cite[Theorem 4]{necoara_linear_2019}, and \cite[Theorem 7]{necoara_linear_2019}, it satisfies error bound condition as given in Assumption \ref{ass:pg-eb}, hence Assumption \ref{ass:lin-cnvg-for-pp} also. 
            \par
            Let $\mu_f = \Vert A\Vert^2/\kappa_f$, let $\kappa_f = \theta^{-2}(A, C)$ be the Hoffman Constant as presented by Necoara et al. in \cite[Section 4]{necoara_linear_2019} where $C$ is the constraint matrix of the inequality set $\delta(z | \{x : \Vert x\Vert_1 \le 1\})$, then the error bound constant can be satisfied with
            \begin{align*}
                \gamma_\lambda = \frac{\kappa_f}{1 + \lambda\mu_f + \sqrt{1 + \lambda\mu_f}}. 
            \end{align*}
        \end{proof}
        \begin{remark}
            It is very difficult to obtain a lower estimate for $\gamma$ in practice. 
        \end{remark}
        \begin{definition}[piecewise linear-quadratic function {\cite[Definition 10.20]{rockafellar_variational_1998}}]
            A function $f: \RR^n \rightarrow \overline \RR$ is piecewise linear-quadratic when $\dom f$ is the union of finitely many piecewise polyhedral set, such that on each polyhedral partition of $f$ there exists $\alpha \in \RR, a \in \RR^n$, $C\in \RR^{n \times n}$ as a symmetric matrix is where $f$ has the representation $x \rightarrow \langle x, Cx\rangle + \langle a, x\rangle + c$. 
        \end{definition}
        The following proposition characterizes another case where error bound conditions of problem holds. 
        \begin{proposition}[convex PLQ proximal problem]\label{prop:plq-pp}

@@

            For any integer $k \ge 0$, this assumption is about parameters of the proximal problem $\left(g, \omega, A, \tilde y_k, \Phi_\lambda^{(k)}, \Psi_\lambda^{(k)}, L^{\lambda, (k)}_{\Phi} ,\gamma_\lambda^{(k)}\right)$ introduced at the beginning of this section, iterates $\left(z_j^{(k)}, v_j^{(k)}\right)_{j\ge0}$, the primal dual solutions $\left(\bar z^{(k)}, \bar v^{(k)}\right)$ and additional constants $\lambda^{\min}, \lambda^{\max}, \gamma^{\min}, C_0$. 

@@

                \item The iterates of the inner loop $(z_j^{(k)}, v_j^{(k)})_{k \ge 0}$ are produced by an algorithm that satisfies Definition \ref{def:ista-inner-lp}. 

@@

            Let $\left(g, \omega, A, \tilde y_k, \Phi_\lambda^{(k)}, \Psi_\lambda^{(k)}, L^{\lambda, (k)}_{\Phi} ,\gamma_\lambda^{(k)}\right)$, $\left(z_j^{(k)}, v_{j}^{(k)}\right)_{j \ge 0}$, $\left(\bar z^{(k)}, \bar v^{(k)}\right)$ and additional parameters $\lambda^{\min}, \lambda^{\max}, \gamma^{\min}, C_0$ such that they satisfy Assumption \ref{ass:bounded-inn-cmplx}. 

@@

                Denote $N_\epsilon$ to be the total number of iteration of inner loop needed to achieve $\mathbf G_\lambda^{(k)}(z_j, v_j) \le \epsilon$, then it's sufficient to have 

@@

                & \mathbf G_\lambda^{(k)}(z_j^{(k)}, v_j^{(k)}) 

@@

                \right)^{j/2}

@@

                \right)^{j/2} C_2

@@

                \right)^{j/2} C_2. 

@@

            Now, substitute $j = N_\epsilon$ then it's prominent that $\mathbf G_\lambda^{(k)}\left(z_j^{(k)}, v_j^{(k)}\right) \le \epsilon$ by using the log of base formula. 

@@

\appendix
    \section{Super boring chores}
        Super boring stuff that I just want to skip but somehow necessary. 
        \begin{lemma}[That conjugate for the dual of proximal problem]\;\label{lemma:chore1}\\
            Let $f:\RR^n \rightarrow \overline \RR:= \frac{1}{2\lambda}\Vert u - v\Vert^2$, then its conjugate is given by
            \begin{align*}
                f^\star(v) = \frac{1}{2\lambda}\Vert \lambda v + y\Vert^2 - \frac{1}{2\lambda}\Vert y\Vert^2. 
            \end{align*}
        \end{lemma}
        \begin{proof}
            Recall the following properties for any closed, proper convex function $f: \RR^n \rightarrow \overline \RR$. 
            Let $a \in \RR^n$ be any vector, let $\alpha \in \RR, c \in\RR$ be some scalar, then we have these three properties of conjugating convex funtion. 
            \begin{enumerate}[nosep]
                \item $(\alpha f)^\star = \alpha f^\star \circ (\alpha^{-1}I)$. 
                \item $(f + c)^\star(y) = f^\star(y) - c$. 
                \item $\left(x \mapsto f(x) + \langle x, y\rangle\right)^\star(y) = f^\star(y - a)$. 
            \end{enumerate}
            From here we have: 
            \begin{align*}
                f^\star(v) 
                &= 
                \left(
                   u \mapsto \lambda^{-1}\left(\frac{1}{2}\Vert u\Vert^2 - \langle u, y\rangle\right) 
                    + \frac{1}{2\lambda} \Vert y\Vert^2
                \right)^\star(v)
                \\
                &= \left(
                    u \mapsto \lambda^{-1}\left(\frac{1}{2}\Vert u\Vert^2 - \langle u, y\rangle\right) 
                \right)^\star(v)
                - \frac{1}{2\lambda} \Vert y\Vert^2
                \\
                &= 
                \left[
                    \lambda^{-1}\left(
                    u \mapsto \left(\frac{1}{2}\Vert u\Vert^2 - \langle u, y\rangle\right) 
                \right)^\star\circ(\lambda I)
                \right](v)
                - \frac{1}{2\lambda} \Vert y\Vert^2
                \\
                &= \left[
                    \lambda^{-1}\left(
                    u \mapsto \left(
                        \frac{\Vert \cdot\Vert^2}{2}
                    \right)^\star(u + y)
                \right)\circ(\lambda I)
                \right](v)
                - \frac{1}{2\lambda} \Vert y\Vert^2
                \\
                &= \left[
                    \lambda^{-1}\left(
                        u \mapsto \frac{\Vert u + y\Vert^2}{2}
                    \right)\circ(\lambda I)
                \right](v)
                - \frac{1}{2\lambda} \Vert y\Vert^2
                \\
                &= \lambda^{-1}\left(
                    \frac{1}{2}\Vert \lambda v + y\Vert^2
                \right) 
                - \frac{1}{2\lambda} \Vert y\Vert^2. 
            \end{align*}
        \end{proof}
